\emph{Light Exposure Behavior Assessment (LEBA)}: Develop of a novel instrument to capture light exposure-related behaviours

### 2021-09-15 manuscript.Rmd

# Plots ####
## F1 Plots ####
F1_OCC <- plot(F1_fit, type = "trace", facet =T, main = "Blue Filter OCC")
F1_info <- plot(F1_fit, type = "infoSE", main = "Blue Filter Test Information")
F1_iteminfo <- plot(F1_fit, type = "infotrace", 
                    facet_items = T, main = NULL)

## F2 Plots ####
F2_OCC <- plot(F2_fit, type = "trace", facet =T, main = "Natural Light OCC")
F2_info <- plot(F2_fit, type = "infoSE", main = "Natural Light Test Information")
F2_iteminfo <- plot(F2_fit, type = "infotrace", facet_items = T, main = NULL)

## F3 Plots ####
F3_OCC <-plot(F3_fit, type = "trace", facet =T, main = "Smart Device OCC")
F3_info <- plot(F3_fit, type = "infoSE", main = "Smart Device Test Information")
F3_iteminfo <- plot(F3_fit, type = "infotrace", 
                    facet_items = T, main = NULL)

## F4 Plots ####
F4_OCC <-plot(F4_fit, type = "trace", facet =T, main = "Sleep Environment OCC")
F4_info <- plot(F4_fit, type = "infoSE", main = "Sleep Environment Test Information")
F4_iteminfo <- plot(F4_fit, type = "infotrace", facet_items = T,main = NULL)

## F5 Plots ####
F5_OCC <-plot(F5_fit, type = "trace", facet =T, main = "Electric Light OCC")
F5_info <- plot(F5_fit, type = "infoSE", main = "Electric Light Test Information")
F5_iteminfo <- plot(F5_fit, type = "infotrace", facet_items = T,main = NULL)

@@

```{r Iteminformationcurve, fig.cap="Item information curves (A) blue filter (B) natural light (C)smart device (D)sleep environment (E)electic light", warning=FALSE, out.width="120%", out.height="150%"}
plot_grid(F1_iteminfo, F2_iteminfo,F3_iteminfo,F4_iteminfo,F5_iteminfo, 
          labels = c('A', 'B','C', 'D', 'E' ), label_size = 10 )

>>>>

# Plots ####
## F1 Plots ####
F1_OCC <- plot(F1_fit, type = "trace", facet =T, main = "Blue Filter OCC")
F1_info <- plot(F1_fit, type = "infoSE", main = "Blue Filter Test Information")
F1_iteminfo <- plot(F1_fit, type = "infotrace", 
                    facet_items = T, main = "Blue Filter")

## F2 Plots ####
F2_OCC <- plot(F2_fit, type = "trace", facet =T, main = "Natural Light OCC")
F2_info <- plot(F2_fit, type = "infoSE", main = "Natural Light Test Information")
F2_iteminfo <- plot(F2_fit, type = "infotrace", facet_items = T, main = "Natural Light")

## F3 Plots ####
F3_OCC <-plot(F3_fit, type = "trace", facet =T, main = "Smart Device OCC")
F3_info <- plot(F3_fit, type = "infoSE", main = "Smart Device Test Information")
F3_iteminfo <- plot(F3_fit, type = "infotrace", 
                    facet_items = T, main = "Smart Device")

## F4 Plots ####
F4_OCC <-plot(F4_fit, type = "trace", facet =T, main = "Sleep Environment OCC")
F4_info <- plot(F4_fit, type = "infoSE", main = "Sleep Environment Test Information")
F4_iteminfo <- plot(F4_fit, type = "infotrace", facet_items = T,main = "Sleep Environment")

## F5 Plots ####
F5_OCC <-plot(F5_fit, type = "trace", facet =T, main = "Electric Light OCC")
F5_info <- plot(F5_fit, type = "infoSE", main = "Electric Light Test Information")
F5_iteminfo <- plot(F5_fit, type = "infotrace", facet_items = T,main = "Electric Light")

@@

```{r Iteminformationcurve, fig.cap="Item information curves (A) blue filter (B) natural light (C)smart device (D)sleep environment (E)electic light", warning=FALSE, out.width="100%", out.height="120%"}
plot_grid(F1_iteminfo, F2_iteminfo,F3_iteminfo,F4_iteminfo,F5_iteminfo, 
          labels = c('A', 'B','C', 'D', 'E' ), label_size = 10 )
